tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-10-01 chapter3_results_bergheiPir/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Heatmap of individual gene comps
Reverse order of comparisons in Qusage heatmap

@@

```{r post48livvearlyliv}

post48livvearlyliv <- lapply(
  list(pir_geneset,
    ShortLong_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Liv.post48h-Liv.24h',
                                gene_list,
                                n.points = 2^18)

    list(results = qs.results.subfam, 
         qstable = qsTable(qs.results.subfam) %>% 
           mutate(contrast = qs.results.subfam$contrast))
  }
)

lapply(post48livvearlyliv, function(x) `$`(x,qstable))
```

@@

comparisons <- c(
  unlist(
    lapply(seq_along(ordered_stages),
           function(i){ if(i < length(ordered_stages)){ paste0(ordered_stages[i],'-',ordered_stages[i+1]) } }
    )
  ),
  'Liv.post48h-Liv.24h',
  'Asex.Schiz-Gam.Male',
  'Ook-Sporoz',
  'Gam.Male-Asex.Mixed',
  'Gam.Male-Liv.Meroz'
)

@@

all_stats_df <- lapply(all_comparisons, getElement, 'combined') %>% 
  bind_rows %>% 
  mutate(fdr_r = p.adjust(p.Value, method = 'fdr')) %>% 
  arrange(fdr_r)

all_stats_df <- all_stats_df[order(match(all_stats_df$pathway.name,order_path.names)),]

@@

all_stats_df_cast <- all_stats_df_cast[ordering(rownames(all_stats_df_cast),
                                                r_order_vector),
                                       order_path.names]
png(filename = "plots/thesis_chapter3_figure_statsCompHeatmap_geneGroups.png",
    width = 7,
    height = 5,
    units = "in",
    res = 330)
Heatmap(all_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          fdr_val <- all_stats_df[
            all_stats_df$contrast == rownames(all_stats_df_cast[i,]),
          ]$fdr_r[j]
          if(fdr_val<= 0.05){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10,
                        fontface = 'bold')
            )
          }
        })
dev.off()
```

>>>>

order_path.names <- ordering(c('pirs', unique(pir_info$SorL), unique(pir_info$clade)), 
                             order_vector = c('pir','L','S'))

@@

Edit to not do FDR again for all comparisons together, and reversing the order of labels/logFoldchanges to better match actual transitions.

@@

comparisons <- c(
  unlist(
    lapply(seq_along(ordered_stages),
           function(i){ if(i < length(ordered_stages)){ paste0(ordered_stages[i+1],'-',ordered_stages[i]) } }
    )
  ),
  'Liv.post48h-Liv.24h',
  'Asex.Schiz-Gam.Male',
  'Ook-Sporoz',
  'Gam.Male-Asex.Mixed',
  'Gam.Male-Liv.Meroz'
)

@@

all_stats_df <- lapply(all_comparisons, getElement, 'combined') %>% 
  bind_rows

@@

all_stats_df_cast <- all_stats_df_cast[ordering(rownames(all_stats_df_cast),
                                                r_order_vector),
                                       order(match(colnames(all_stats_df_cast), 
                                                   order_path.names))]

png(filename = "plots/thesis_chapter3_figure_statsCompHeatmap_geneGroups.png",
    width = 7,
    height = 5,
    units = "in",
    res = 330)
Heatmap(all_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          stat_df <- all_stats_df[all_stats_df$contrast == rownames(all_stats_df_cast[i,]),]
          fdr_val <- stat_df$FDR[j]
          logfold <- stat_df$log.fold.change[j]
          if(fdr_val<= 0.05){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10,
                        fontface = 'bold',
                        col = ifelse(logfold > 2, 'white', 'black'))
            )
          }
        })
dev.off()
```
